\documentclass{article}
\usepackage{graphicx}
\setlength\parindent{0pt}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Test Plan\\Space Pinball 2017}

\author{Team \#17, Problem Statement
		\\ Andrew Bennett 1319879
		\\ Kyriakos Kyprianou  400025691
		\\ Teodor Tomescu 400038361
}

\date{}


\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Sep. 27th -- Rev0.1 	& Andrew, Kyriakos, Teodor & first draft \\
Dec. 6th  -- Rev1		& Andrew, Kyriakos, Teodor & added revision history table and title page.\\

\bottomrule
\end{tabularx}
\end{table}

\newpage
\maketitle
\newpage

\section{Problem Statement}
\subsection{What problem are you trying to solve?}

Today, many people use video games as a source of entertainment. Their popularity has grown due to the ubiquity of mobile computers, which include phones, tablets, and laptops. Creating an entertaining video game has never had the potential to affect people’s lives like it does today.\\

However, the growing accessibility of video games presents a number of unique challenges to developers. Namely, a well designed video game should have gameplay that is intuitive across diverse user demographics, as well as consistent across the numerous platforms on which it can be ran.\\

The problem we are trying to solve is "How can we create an intuitive, cross platform video game that can be enjoyed by anyone on any device?".


\subsection{Why is this an important problem?}
Developing a video game that can be enjoyed by any demographic is important because everybody should have access to video games that they can enjoy. Creating a video game that can be played by people of different ages and interests is a way to bring people together, foster healthy relationships, and provide entertainment. \\

Developing a video game so that it can be played on any device (cross-platform) is critical in today\textsc{\char13}s society where there are many popular device options each with different operating systems.



\subsection{Context}

Our video game will be an arcade-style pinball game that will be intuitive for any user to play. The game itself will be accessible on any device that can access a modern web browser, specifically any browser that can process HTML5 and WebGL including Chrome, Firefox, Internet Explorer 11 and later, Safari 8 and later, and more. Thus, any modern phone, tablet, laptop, or desktop computer will be able to access our game.  \\

The stakeholders in our project include game developers, mobile developers, web developers, and consumers (players). In addition to these stakeholders, students and developers learning about game development will also be impacted by our project as all of our source code will be published as open source. This will allow anybody to learn from our project or expand upon it.



\end{document}
